### 2017-05-11 manuscript/usses_water_ms.Rmd
adds some more methods

####  Species Synchrony and Species Composition

>>>>

We calculated ecosystem stability as the temporal mean of ANPP divided by its temporal standarad deviation $\left( \overline{\text{ANPP}} / \sigma(\text{ANPP}) \right)$.
Ecosystem stability was calculated for each plot.
We compared ecosystem stability among treatments using ANOVA (same \texttt{R} functions as above).

####  Species Synchrony and Species Composition
We calculated the synchrony of species fluctuations through time using basal area cover data and individual density data.
For both data types we calculated the synchrony metric described by @Loreau2008a, which ranges from 0 (perfect ascynchrony) to 1 (perfect synchrony).
Before calculating synchrony, we averaged cover and density over plots within treatments for each species.
We used the \texttt{synchrony()} function in the \texttt{R} package \texttt{codyn} [@Hallett2016] to calculate species synchrony.

To see if community composition differed among treatments through time, we used non-dimensional multivariate scaling (NMDS) based on Bray-Curtis distances.
For each year of the experiment, we first calculated Bray-Curtis distances among all plots, and then extracted those distances for use in the NMDS.
We plotted the first two axes of NMDS scores to see if community composition overlapped, or not, among treatments in each year.
We used functions in the \texttt{R} package \texttt{vegan} [@Oksanen2016] to calculate Bray-Curtis distances and the run the NMDS analysis.
